Papers

### 2025-12-18 index.qmd
add new preprint

@@

<font color="#d08770">[June 13 2024].</font> **Paper accepted**. Calalo JA, Ngo T, Sullivan S, Strand K, Buggeln JH, Lokesh R, Roth A, Carter MJ, Kurtzer IL, & Cashaback JGA. (Accepted). Online movements reflect ongoing deliberation. *Journal of Neuroscience*. [https://doi.org/10.1523/JNEUROSCI.1913-24.2025](https://doi.org/10.1523/JNEUROSCI.1913-24.2025){target="_blank"}

>>>>

<font color="#d08770">[December 15 2025].</font> **New Preprint**. Calalo JA, Sullivan SR, Muscara NR, Buggeln JH, Ngo TT, Short MM, Carter MJ, Kurtzer IL, & Cashaback JGA. Deliberation is a controllable process governed by desirability and cognitive effort. *bioR$\chi$iv*. [https://doi.org/10.64898/2025.12.12.693733](https://doi.org/10.64898/2025.12.12.693733 ){target="_blank"}

@@

### 2025-12-18 papers.qmd
add new preprint

- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA.. Involuntary feedback responses reflect a representation of partner actions. *bioR$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.1101/2025.07.29.667240){target="_blank" style="color: inherit;"}

@@

- Hussain M., Foglia SD., Park J., Ramdeo KR., Adams FC., Drapeau CC., Bobinski AR., Carter MJ., & Nelson AJ. Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle. *Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_hussain-etal_ipsilateral-contraction-increases-map-area-and-decreases-motor-threshold-for-contralateral-hand-muscle.pdf){target="_blank" style="color: inherit;"}

>>>>

- Calalo JA., Sullivan SR., Muscara NR., Buggeln JH., Ngo TT., Short MM., Carter MJ., Kurtzer IL., & Cashaback JGA. Deliberation is a controllable process governed by desirability and cognitive effort. *bioR$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.64898/2025.12.12.693733){target="_blank" style="color: inherit;"}

- Sullivan SR., Buggeln JH., Calalo JA., Ngo TT., Semrau JA., Carter MJ., & Cashaback JGA. Involuntary feedback responses reflect a representation of partner actions. *bioR$\chi$iv*. --- [{{< ai doi >}}](https://doi.org/10.1101/2025.07.29.667240){target="_blank" style="color: inherit;"}

@@

- Hussain M., Foglia SD., Park J., Ramdeo KR., Adams FC., Drapeau CC., Bobinski AR., Carter MJ., & Nelson AJ. (2025). Ipsilateral contraction increases map area and decreases motor threshold for contralateral hand muscle. *Neuroscience*. ---
[{{< ai doi >}}](https://doi.org/10.1016/j.neuroscience.2025.09.034){target="_blank" style="color: inherit;"}
[{{< fa file-pdf >}}](https://raw.github.com/cartermaclab/carterlab-papers/main/2025_hussain-etal_ipsilateral-contraction-increases-map-area-and-decreases-motor-threshold-for-contralateral-hand-muscle.pdf){target="_blank" style="color: inherit;"}
